Numerical trajectory patterns of floating macroalgae

### 2020-09-30 thesis_chapter_3.Rmd
script for extra datasets added

p_RK4$type <- "RK4" # add extra column 'type' to dataframe and assigned 'passive' label

>>>>

p_RK4$type <- "RK4" # add extra column 'type' to dataframe and assigned 'RK4' label

p_EE <- tidync("OceanParcels/trajectory_data/PassiveFloat.nc") %>%
  hyper_tibble() %>%
  dplyr::select(lon, lat, time, distance, age) %>%
  dplyr::rename(t = time) %>%
  mutate(t = as.POSIXct(t, origin = "2002-01-01 00:00:00"))

p_EE_mean <- p_EE %>% # summarise data based on time 
   group_by(t) %>% 
   summarise_all(funs(mean = mean, sd = sd, min = min, max = max), na.rm = T)

p_EE$type <- "EE" # add extra column 'type' to dataframe and assigned 'EE' label
